Dynamic Species Interactions in the San Nicolas Island Kelp Forest

### 2018-06-08 EDM_SNI_analysis.Rmd
edited results language

* **Temperature**
    + Elevated SST has similar effects to nutrient stress (elevated MEI and PDO, and reduced NPGO), which makes sense: In Southern California, elevated SST is associated with reduced nutrient availability[@Zimmerman1984,@Bell2015]. Similar effects as described above for nutrient stress hold for elevated temperature.

>>>>

* **Temperature**
    + Elevated SST has similar effects to nutrient stress (elevated MEI and PDO, and reduced NPGO), which makes sense: In Southern California, elevated SST is associated with reduced nutrient availability[@Zimmerman1984,@Bell2015]. Similar effects as described above for nutrient stress (at least as measured by the large oceanographic indices) hold for elevated temperature. This suggests both that this type of effect manifests at multiple temporal scales, and that the combination of elevated temperature and stressful nutrient regimes could have compounding effects on species interactions and ecosystem dynamics.
